Estimation below the detection limit

### 2018-04-12 TEX/draft2.tex
Investigating which moments we really should be taking, because of inconsistencies between paper and code

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
\begin{equation} \label{eq:ac_general}
a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
\end{equation}
Explicitly, the first three autocorrelations are
\begin{align} \label{eq:autocorrelations}
a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. 
Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.

@@

The main pillar of this work is the following simple observation.
If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
to a scaled, biased, version of the signal's autocorrelation:
\begin{align}
\lim_{N\to\infty} a_y^1 &= \gamma a_{x}^1, \nonumber\\
\lim_{N\to\infty} a_y^2[\ell] &= \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]), \nonumber
\end{align}
for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
These relations are proven in Appendix~\ref{sec:autocorrelation_computation}. The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a particular caution should be taken with the statistical dependencies of the noise entries. 
The relations~\eqref{eq:data_ac_k1}, together with Proposition~\ref{prop:uniqueness}, imply that given $M$ and $\sigma$, one can estimate the signal for any noise level if $M$ is large enough. Next, we show that  $M$ and $\sigma$ are also uniquely determined from the autocorrelations.

>>>>

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
\begin{equation} \label{eq:ac_general}
a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
\end{equation}
Explicitly, the first three autocorrelations are
\begin{align} \label{eq:autocorrelations}
a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. \TODO{We also have $a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]$ -- is that intended? Do we really have symmetry with the negative signs? I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$}
Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.

@@

The main pillar of this work is the following simple observation.
If the support $s$ satisfies the spacing constraint~\eqref{eq:spacing}, then the first $L$ entries of the data autocorrelations converge 
to a scaled, biased, version of the signal's autocorrelation:
\begin{align}
\lim_{N\to\infty} a_y^1 & = \gamma a_{x}^1, \nonumber\\
\lim_{N\to\infty} a_y^2[\ell] & = \gamma a_{x}^2[\ell] +\sigma^2\delta[\ell], \label{eq:data_ac_k1} \\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] & = \gamma a_{x}^3[\ell_1,\ell_2] + \sigma^2\gamma a_{x}^1 \big(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]\big), \nonumber
\end{align}
for $\ell,\ell_1,\ell_2=0,\ldots L-1$, and where $\delta$ denotes the Kronecker delta function. 
These relations are proven in Appendix~\ref{sec:autocorrelation_computation}. The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a particular caution should be taken with the statistical dependencies of the noise entries. 
The relations~\eqref{eq:data_ac_k1}, together with Proposition~\ref{prop:uniqueness}, imply that given $M$ and $\sigma$, one can estimate the signal for any noise level if $M$ is large enough. Next, we show that  $M$ and $\sigma$ are also uniquely determined from the autocorrelations.
